There once was a grid at ol' Carkeek

### 2016-04-14 Manuscript/v0.0/carkeek_grid.tex
add correct pam plot
improve PAM output
tried clustering on spatially invariant taxa

\subsection*{Community Analysis}
% Used k-medoids (PAM) rather than k-means because it does not require euclidean distances can be computed and that the observations follow a gaussian distribution
% because of the nature of our data (lots of zeros, with some very high counts), the mean is not very informative
We simultaneously assessed the existence of distinct community types and the membership of samples to those community types using a partitioning around mediods algorithm (CITE PAM, sometimes referred to as k-mediods clustering), as implemented in the R package fpc (CITE fpc).
The classification of samples to communities was made on the basis of their pairwise Bray-Curtis dissimilarity, calculated using the function vegdist in the R package vegan (CITE VEGAN). % consider Gower distance

@@

\subsection*{Community Analysis}

@@

@@

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{../../Figures/medoids_in_space.pdf}
    \caption{Geographic position of collected samples, colored by membership to clusters identified by partitioning around medoids algorithm. Points are jittered in both horizontal and vertical dimension to distinguish among four replicate PCR products sequenced from each environmental sample.}
  \label{clustering_map} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

>>>>

\subsection*{Community Analysis}
% Used k-medoids (PAM) rather than k-means because it does not require euclidean distances can be computed and that the observations follow a gaussian distribution
% because of the nature of our data (lots of zeros, with some very high counts), the mean is not very informative
We simultaneously assessed the existence of distinct community types and the membership of samples to those community types using a partitioning around mediods algorithm (CITE PAM, sometimes referred to as k-medoids clustering), as implemented in the R package fpc (CITE fpc).
The classification of samples to communities was made on the basis of their pairwise Bray-Curtis dissimilarity, calculated using the function vegdist in the R package vegan (CITE VEGAN). % consider Gower distance

@@

\subsection*{Community Analysis}
Excluding spatially-invariant taxa ?(taxa which occur in only one spatial location) had no discernible effect on the outcome of the PAM analysis (number of clusters, assignment to clusters).

@@

\begin{figure}[h!] % [h!] forces the figure to be placed roughly here
  \centering
    \includegraphics[width=1\textwidth]{../../Figures/pam_in_space.pdf}
    \caption{Geographic position of collected samples, colored by membership to clusters identified by partitioning around medoids algorithm. 
%    Points are jittered in both horizontal and vertical dimension to distinguish among four replicate PCR products sequenced from each environmental sample.
}
  \label{clustering_map} % use this to refer to your figure in the text, so that numbering updates automatically
\end{figure}

@@
